Scottish Child Payment Interventions

### 2024-01-18 minos/outcomes/SCP_vis.Rmd
Adding some WIP plots for poverty statistics

```{r}
source(here::here('minos', 'utils_datain.R'))
#source(here::here('minos', 'utils_validation_vis.R'))
#source(here::here('minos', 'validation', 'utils.r'))
```

```{r}
# out.path <- here::here('output', 'default_config')
# 
# # define subset of variables to reduce size of batch output
# var.list <- c('pidp', 'hidp', 'time', 'weight', 
#               'age', 'ethnicity', 'education_state', 'region', 'nkids',
#               'hh_income',
#               'housing_quality', 'neighbourhood_safety', 'loneliness', 'ncigs', 'nutrition_quality', 'financial_situation', 'urban', 'housing_tenure',
#               'SF_12', 'matdep_child')
# 
# base <- read_output(out.path, 
#                     scenario = 'baseline', 
#                     var.list = var.list,
#                     verbose = TRUE)
# int25All <- read_output(out.path, 
#                         scenario = '25All', 
#                         var.list = var.list,
#                         verbose = TRUE)
# int50All <- read_output(out.path, 
#                         scenario = '50All', 
#                         var.list = var.list,
#                         verbose = TRUE)
# int75All <- read_output(out.path, 
#                         scenario = '75All', 
#                         var.list = var.list,
#                         verbose = TRUE)
# int100All <- read_output(out.path, 
#                         scenario = '100All', 
#                         var.list = var.list,
#                         verbose = TRUE)
# 
# int.list <- c(int25All, int50All, int75All, int100All)
# 
# # set up a boolean tag for batch or not
# # this is necessary because batch runs need slightly different processing before visualisation
# if ('run_id' %in% names(base)) {
#   batch <- TRUE
# } else {
#   batch <- FALSE
# }
# 
# # Save path and save flag
# save.path <- here::here('plots', 'SCOTGOV', 'CPR')
# create.if.not.exists(save.path)
# shall.we.save <- FALSE
# plot.width <- 10
# plot.height <- 5
```

@@

@@

```{r}
sample_information_single <- function(int.dat, int.name, target.year) {
  hh_boosted <- int.dat %>%
    select(hidp, time, income_boosted, boost_amount, nkids) %>%
    filter(income_boosted == 'True') %>%
    group_by(time) %>%
    summarise(n_boosted = length(unique(hidp)),
              total_boost = sum(boost_amount),
              kids_boosted = sum(nkids))

@@

sample_information_batch <- function(int.dat, int.name, target.year) {
  hh_boosted <- int.dat %>%
    select(hidp, time, run_id, income_boosted, boost_amount, nkids) %>%
    filter(income_boosted == 'True') %>%
    group_by(time, run_id) %>%
    summarise(n_boosted = length(unique(hidp)),
              total_boost = sum(boost_amount),
              kids_boosted = sum(nkids))

@@

```{r}
if (batch) {
  sample_information_batch(int25, int.name = 'int25', target.year = 2030)
} else {
  sample_information_single(int25, int.name = 'int25', target.year = 2030)
}
```

@@

```{r}
if (batch) {
  sample_information_batch(int35, int.name = 'int35', target.year = 2030)
} else {
  sample_information_single(int35, int.name = 'int35', target.year = 2030)
}
```

@@

```{r}
if (batch) {
  sample_information_batch(int45, int.name = 'int45', target.year = 2030)
} else {
  sample_information_single(int45, int.name = 'int45', target.year = 2030)
}
```

## TESTING

>>>>

```{r}
source(here::here('minos', 'utils_datain.R'))
```

@@

# Poverty Statistics

See how interventions affect child poverty.

## Relative Poverty

```{r}
# First need the relative poverty thresholds from baseline
threshold <- base %>%
  select(time, weight, hh_income) %>%
  group_by(time) %>%
  summarise(poverty_threshold = (weighted.mean(hh_income, w = weight) * 0.6))

ggplot(data = threshold, aes(x = time, y = poverty_threshold)) +
  geom_col() +
  labs(title = 'Relative poverty threshold over time') +
  xlab('Year') +
  ylab('Threshold')
```

```{r}
int25.test <- merge(int25, threshold, by = 'time')
# Now calculate number of households and number of children below threshold
hh_boosted <- int25.test %>%
  select(hidp, time, hh_income, income_boosted, boost_amount, nkids, poverty_threshold) %>%
  filter(income_boosted == 'True') %>%
  filter(hh_income < poverty_threshold) %>%
  group_by(time) %>%
  summarise(n = n(),
            n_boosted = length(unique(hidp)),
            total_boost = sum(boost_amount),
            kids_boosted = sum(nkids)) %>%
  mutate(prop_boosted = n_boosted / n,
         prop_kids_boosted)

p1 <- ggplot(hh_boosted, aes(x = time, y = n_boosted)) +
  geom_line() +
  labs(title = 'Number of households receiving intervention', subtitle = int.name) +
  xlab('Year') +
  ylab('Number Boosted')
print(p1)

p2 <- ggplot(hh_boosted, aes(x = time, y = kids_boosted)) +
  geom_line() +
  labs(title = 'Number of children in households receiving intervention', subtitle = int.name) +
  xlab('Year') +
  ylab('Number Children')
print(p2)
```

@@

```{r}
intervention_information_single <- function(int.dat, int.name, target.year) {
  hh_boosted <- int.dat %>%
    select(hidp, time, income_boosted, boost_amount, nkids) %>%
    filter(income_boosted == 'True') %>%
    group_by(time) %>%
    summarise(n_boosted = length(unique(hidp)),
              total_boost = sum(boost_amount),
              kids_boosted = sum(nkids))

@@

intervention_information_batch <- function(int.dat, int.name, target.year) {
  hh_boosted <- int.dat %>%
    select(hidp, time, run_id, income_boosted, boost_amount, nkids) %>%
    filter(income_boosted == 'True') %>%
    group_by(time, run_id) %>%
    summarise(n_boosted = length(unique(hidp)),
              total_boost = sum(boost_amount),
              kids_boosted = sum(nkids))

@@

```{r}
if (batch) {
  intervention_information_batch(int25, int.name = 'int25', target.year = 2030)
} else {
  intervention_information_single(int25, int.name = 'int25', target.year = 2030)
}
```

## 30

```{r}
if (batch) {
  intervention_information_batch(int30, int.name = 'int30', target.year = 2030)
} else {
  intervention_information_single(int30, int.name = 'int30', target.year = 2030)
}
```

@@

```{r}
if (batch) {
  intervention_information_batch(int35, int.name = 'int35', target.year = 2030)
} else {
  intervention_information_single(int35, int.name = 'int35', target.year = 2030)
}
```

## 40

```{r}
if (batch) {
  intervention_information_batch(int40, int.name = 'int40', target.year = 2030)
} else {
  intervention_information_single(int40, int.name = 'int40', target.year = 2030)
}
```

@@

```{r}
if (batch) {
  intervention_information_batch(int45, int.name = 'int45', target.year = 2030)
} else {
  intervention_information_single(int45, int.name = 'int45', target.year = 2030)
}
```

## 50

```{r}
if (batch) {
  intervention_information_batch(int50, int.name = 'int50', target.year = 2030)
} else {
  intervention_information_single(int50, int.name = 'int50', target.year = 2030)
}
```

# TESTING
